Longitudinal Principal Manifold Estimation

### 2024-04-04 paper/main.tex
include regression-adjusted results and update caption

\begin{table}[ht]
  \centering
  \begin{tabular}{|c c c c|}
    \hline
    Structure & Data & LPME & PME  \\
    \hline
    Left Hippocampus & 218 & 225 & 191 \\
    Right Hippocampus & 221 & 245 & 195 \\
    Left Thalamus & 82.9 & 49.7 & 72.0 \\
    Right Thalamus & 147 & 116 & 130 \\
    \hline
  \end{tabular}
  \caption{Mean of the empirical standard deviation of volume estimates computed for each ADNI participant.}
  \label{table:adni_volume_sds}
\end{table}

>>>>

\begin{table}[ht]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Structure & Regression-Adjusted & Data & LPME & PME  \\
    \hline
    Left Hippocampus & No & 218 & 225 & 191 \\
    Right Hippocampus & No & 221 & 245 & 195 \\
    Left Thalamus & No & 82.9 & 49.7 & 72.0 \\
    Right Thalamus & No & 147 & 116 & 130 \\
    Left Hippocampus & Yes & 184 & 197 & 160 \\
    Right Hippocampus & Yes & 185 & 215 & 163 \\
    Left Thalamus & Yes & 68.3 & 30.7 & 57.9 \\
    Right Thalamus & Yes & 124 & 89.9 & 109 \\
    \hline
  \end{tabular}
  \caption{Mean of the empirical standard deviation of volume estimates computed for each ADNI participant. Entries that were not regression-adjusted include computations for raw volume estimates, while regression-adjusted entries compute the standard deviations of linear regression models regressing the volume estimates on time.}
  \label{table:adni_volume_sds}
\end{table}
